Multi-channel Kondo model URG

### 2021-12-13 notes/multi-channel-urg.tex
obtained all processes for the spin-S multichannel RG

\documentclass[12pt]{revtex4-2}
\usepackage{braket,amsmath,amssymb,graphicx,float,paralist,color}
\usepackage[hidelinks]{hyperref}
\allowdisplaybreaks
\begin{document}
\title{Multi-channel Kondo model URG}
\author{Abhirup Mukherjee}
\date{\today}
\maketitle
\tableofcontents
\section{Introduction of the Hamiltonian and its zero mode}
The isotropic multi-channel Kondo model~\cite{Noz_blandin_1980,Gan_Andrei_Coleman_1993,emery_kivelson,Gan_mchannel_1994,Tsvelick_Weigmann_mchannel_1984,Tsvelick_weigmann_mchannel_1985,parcollet_olivier_large_N,kimura_taro_Su_N_kondo,PhysRevB.73.224445,cox_jarrell_two_channel_rev,affleck_1991_overscreen,Coleman_tsvelik,affleck1993exact} is described by the Hamiltonian
\begin{align}
	\label{mc_ham}
	H = \sum_{k,\alpha,\gamma}\epsilon_{k}^\gamma \hat n^\gamma_{k\alpha} + J\sum_{kk^\prime,\gamma} \vec{S_d}\cdot\vec{s}_{\alpha\alpha^\prime}{c^\gamma_{k\alpha}}^\dagger c^\gamma_{k^\prime\alpha^\prime}~.
\end{align}
In the above equation, \(k,k^\prime\) sum over the momentum states, \(\alpha,\alpha^\prime\) sum over the spin indices and \(\gamma\) sums over the various channels. \(\vec S_d, \vec s\) are the impurity and conduction bath spin vectors. The presence of a common spin-exchange coupling \(J\) for all the channels is what makes the problem isotropic with respect to the channels.

@@

@@

% We will use the relations:
% \begin{equation}\begin{aligned}
% 	S_d^\pm S_d^z &= S_d^z S_d^\pm \mp S_d^\pm\\
% 	S_d^z S_d^\pm &= S_d^\pm S_d^z \pm S_d^\pm\\
% 	S_d^\pm S_d^\mp &= \vec S_d^2 - {S_d^z}^2 \pm S_d^z
% \end{aligned}\end{equation}
The various terms that renormalize the Hamiltonian can be described in terms of the bath spin operators that come into them. For example, the term that has \(s^z\) on both sides of the intervening Greens function can be represented as \(z|z\). There are 7 such terms: \(z|z, \pm|\mp, z|\pm, \pm|z\). Each of these terms occur both in the particle and the hole sectors.

@@

\paragraph{\(-|z\)}
\begin{equation}\begin{aligned}
	\sum_{kk^\prime,m} c^\dagger_{q \downarrow} c_{k^\prime \uparrow} \ket{m+1}\bra{m}\frac{J^\downarrow_{m}{J^t_m}}{\omega - D/2 - \frac{J}{2}S_d^z}\ket{m}\bra{m} c^\dagger_{k \downarrow}c_{q \downarrow} = -n_{q \downarrow}\sum_{kk^\prime,m}\frac{J^\downarrow_{m} J^t_m c^\dagger_{k \downarrow}c_{k^\prime\uparrow} \ket{m+1}\bra{m}}{\omega_{m, \uparrow} - D/2 - \frac{J}{2}(m)}
\end{aligned}\end{equation}
The first four terms renormalize \(J^\sigma_m\):
\begin{equation}\begin{aligned}
	\Delta J^\sigma_{m} = -\frac{\left( J^\sigma_m \right) ^2 + \left( J^t_{m-\frac{1+\sigma}{2}} \right) ^2}{\omega - D/2 + J/4}
\end{aligned}\end{equation}
Here, we have defined \(J^t_m = 0\) for \( |m| > S\). Two relations can be obtained from this RG equation, the RG equations for the sum and difference of the couplings. These sum and difference are defined by rewriting the Ising part of the Hamiltonian in the following fashion:
\begin{equation}\begin{aligned}
	\sum_{m=-S}^S \sum_{kl,\atop{\sigma=\uparrow,\downarrow}} J^\sigma_m \ket{m}\bra{m} c^\dagger_{k \sigma}c_{l \sigma} = \sum_{m=-S}^S \sum_{\sigma=\uparrow,\downarrow} J^+_m \ket{m}\bra{m} \sum_\sigma \hat n_{0\sigma}  + \sum_{m=-S}^S J^-_m \ket{m}\bra{m} 2s^z_0
\end{aligned}\end{equation}
where \(2J^\pm_m = J^\uparrow_m \pm J^\downarrow_m\).
The RG equation for the sum of the couplings is
\begin{equation}\begin{aligned}
	\Delta J^+_m = -\frac{1}{2}\frac{\sum_\sigma \left( J^\sigma_m \right) ^2 + \sum_\sigma \left( J^t_{m-\frac{1+\sigma}{2}} \right) ^2}{\omega - D/2 + J/4} = -\frac{J^2}{4}\frac{S(S+1)}{\omega - D/2 + J/4}
\end{aligned}\end{equation}
This is an \(m-\)independent piece, so it can be summed over to produce an impurity-independent potential scattering term:
\begin{equation}\begin{aligned}
	\sum_{m=-S}^S \sum_{\sigma=\uparrow,\downarrow} J^+ \ket{m}\bra{m} \sum_\sigma \hat n_{0\sigma} = J^+ \mathbb{I}\sum_\sigma \hat n_{0\sigma}
\end{aligned}\end{equation}
Since this term does not have any Kondo physics, we drop this piece and say that \(\Delta J^+ = 0\) and so \(\Delta J^\uparrow_m = - \Delta J^\downarrow_m \implies J^\uparrow_m = -J^\downarrow_m\) throughout the RG flow.

>>>>

\documentclass{revtex4-2}
\usepackage{braket,amsmath,amssymb,graphicx,float,paralist,color}
\usepackage[hidelinks]{hyperref}
\allowdisplaybreaks
\begin{document}
\title{Multi-channel Kondo model URG}
\author{Abhirup Mukherjee}
\date{\today}
\maketitle
\tableofcontents
\section{Introduction of the Hamiltonian and its zero mode}
The isotropic multi-channel Kondo model~\cite{Noz_blandin_1980,Gan_Andrei_Coleman_1993,emery_kivelson,Gan_mchannel_1994,Tsvelick_Weigmann_mchannel_1984,Tsvelick_weigmann_mchannel_1985,parcollet_olivier_large_N,kimura_taro_Su_N_kondo,PhysRevB.73.224445,cox_jarrell_two_channel_rev,affleck_1991_overscreen,Coleman_tsvelik,affleck1993exact} is described by the Hamiltonian
\begin{align}
	\label{mc_ham}
	H = \sum_{k,\alpha,\gamma}\epsilon_{k}^\gamma \hat n^\gamma_{k\alpha} + J\sum_{kk^\prime,\gamma} \vec{S_d}\cdot\vec{s}_{\alpha\alpha^\prime}{c^\gamma_{k\alpha}}^\dagger c^\gamma_{k^\prime\alpha^\prime}~.
\end{align}
In the above equation, \(k,k^\prime\) sum over the momentum states, \(\alpha,\alpha^\prime\) sum over the spin indices and \(\gamma\) sums over the various channels. \(\vec S_d, \vec s\) are the impurity and conduction bath spin vectors. The presence of a common spin-exchange coupling \(J\) for all the channels is what makes the problem isotropic with respect to the channels.

@@

\section{Derivation of URG equations for the multi-channel spin-\(S\) impurity Kondo model}
The leading order renormalization is the same as the single-channel model, and is shown in the appendix. Following that calculation, the Hamiltonian we will work with is 
\begin{equation}\begin{aligned}
		    H = \sum_{k\sigma}\epsilon_{k}\tau_{k\sigma} + \sum_{m=-S}^S \sum_{kl,\atop{\sigma=\uparrow,\downarrow}} J^\sigma_m \ket{m}\bra{m} c^\dagger_{k \sigma}c_{l \sigma} + \sum_{kl} \sum_{m=-S}^{S-1} J^t_{m} \left(\ket{m+1}\bra{m} s^-_{kl}  + \text{h.c.}\right)
\end{aligned}\end{equation}
where \(\left\{\ket{m}\right\} \) are the eigenstates of \(S_d^z\), \(J^\sigma_m = \frac{1}{2} \sigma m J\) in the UV Hamiltonian, and \(J^t_{m} = J\frac{1}{2}\sqrt{S(S+1) - m(m+1)}\) is the coupling that connects \(\ket{m}\) and \(\ket{m+1}\).

The next order renormalization is of the form
\begin{equation}\begin{aligned}
	\Delta H^{(3)}_j = \underbrace{c^\dagger T \frac{1}{\omega^\prime - H_D} H_X \frac{1}{\omega^\prime - H_D} T^\dagger c}_\text{first term (particle sector)} ~+~ \underbrace{T^\dagger c \frac{1}{\omega - H_D} H_X \frac{1}{\omega - H_D} c^\dagger T}_\text{second term (hole sector)}
\end{aligned}\end{equation}

Before we start, we will make another simplification. A general term of \(\Delta H\) will be of the form
\begin{equation}\begin{aligned}
	\sum_{q,k,l_1} c^\dagger_{q\beta, l_1}c_{k \alpha, l_1}\ket{m_1}\bra{m_2} \frac{1}{\omega - \frac{D}{2} - \frac{\epsilon_k}{2} + \frac{\beta J}{4}S_d^z} \ket{m_2} c^\dagger_{k_1 \sigma_1, l_2}c_{k_2 \sigma_2,l_2} \bra{m_3}\frac{1}{\omega - \frac{D}{2} - \frac{\epsilon_k}{2} + \frac{\beta J}{4}S_d^z}\ket{m_3}\bra{m_4}c^\dagger_{k\alpha, l_1}c_{q\beta, l_1}
\end{aligned}\end{equation}
We have not bothered to write all the summations and the couplings correctly, because we will only simplify the denominator here. Evaluating the inner products gives
\begin{equation}\begin{aligned}
	\ket{m_1}\bra{m_4}\sum_k c^\dagger_{q\beta}c_{k \alpha} \frac{1}{\omega_{m_2,\beta} - \frac{D}{2} - \frac{\epsilon_k}{2} + \frac{\beta J m_2}{4}}  c^\dagger_{k_1 \sigma_1, l_2}c_{k_2 \sigma_2,l_2} \frac{1}{\omega_{m_3,\beta} - \frac{D}{2} - \frac{\epsilon_k}{2} + \frac{\beta J m_3}{4}}c^\dagger_{k\alpha}c_{q\beta}
\end{aligned}\end{equation}
To compare with the spin-\(\frac{1}{2}\) RG equations, we will transform the general spin-\(S\) \(\omega\) to the spin-\(\frac{1}{2}\) \( \omega\), using \(\omega_{m,\sigma} \to \omega - \frac{J}{2}\left(m\sigma - \frac{1}{2}\right)\).
\begin{equation}\begin{aligned}
	\hat n_{q\beta}\ket{m_1}\bra{m_4}c^\dagger_{k_1 \sigma_1, l_2}c_{k_2 \sigma_2,l_2}\sum_k \left( 1 - \hat n_{k\alpha} \right) \left(\frac{1}{\omega - \frac{D}{2} - \frac{\epsilon_k}{2} + \frac{J}{4}}\right)^2  
\end{aligned}\end{equation}
We can set \(\sum_q \hat n_{q\beta} = n(D)\). Performing the sums over \(k\) and \(l_1\) in the same fashion as previously gives
\begin{equation}\begin{aligned}
	-\frac{1}{2}\ket{m_1}\bra{m_4}c^\dagger_{k_1 \sigma_1, l_2}c_{k_2 \sigma_2,l_2} \frac{\rho n(D) K}{\omega - \frac{D}{2} + \frac{J}{4}}
\end{aligned}\end{equation}
Reinstating the complete summation and the couplings gives
\begin{equation}\begin{aligned}
	-\frac{1}{2}\frac{\rho n(D) K}{\omega - \frac{D}{2} + \frac{J}{4}}\sum_{m_1,m_4}\sum_{k_1,k_2,l_2,\sigma_1\sigma_2}\lambda_{1}\lambda_{2}\lambda_{3}\ket{m_1}\bra{m_4}c^\dagger_{k_1 \sigma_1, l_2}c_{k_2 \sigma_2,l_2}
\end{aligned}\end{equation}
There is no sum over \(m_2\) and \(m_3\) because they are constrained by \(m_1\) and \(m_4\) respectively. \(\lambda_i\) represent the couplings present at the three interaction vertices.

The various terms in each sector can be represented as \(a|b|c\), where \(a,b,c \in \left\{z,+,-\right\} \) and represent the operator for the conduction electrons in the three stages. We will only calculate the terms in the particle sector, the ones in hole sector will be equal to these because of particle-hole symmetry.
\paragraph{\(z|z|z\)}
\begin{equation}\begin{aligned}
	- \frac{1}{2}\frac{\rho n(D) K}{\omega - \frac{D}{2} + \frac{J}{4}}\sum_\beta \sum_{m}\sum_{k_1,k_2,l_2,\sigma} \left(J^\beta_m\right)^2 J^\sigma_m \ket{m}\bra{m}c^\dagger_{k_1 \sigma, l_2}c_{k_2 \sigma,l_2}
\end{aligned}\end{equation}

\paragraph{\(-|z|+\)}
\begin{equation}\begin{aligned}
	-\frac{1}{2}\frac{\rho n(D) K}{\omega - \frac{D}{2} + \frac{J}{4}}\sum_{m}\sum_{k_1,k_2,l_2,\sigma} \left( J^t_m \right) ^2 J^\sigma_m \ket{m+1}\bra{m+1}c^\dagger_{k_1 \sigma, l_2}c_{k_2 \sigma,l_2}
\end{aligned}\end{equation}
\paragraph{\(+|z|-\)}
\begin{equation}\begin{aligned}
	-\frac{1}{2}\frac{\rho n(D) K}{\omega - \frac{D}{2} + \frac{J}{4}}\sum_{m}\sum_{k_1,k_2,l_2,\sigma} \left( J^t_m \right) ^2 J^\sigma_{m+1} \ket{m}\bra{m}c^\dagger_{k_1 \sigma, l_2}c_{k_2 \sigma,l_2}
\end{aligned}\end{equation}
\paragraph{\(+|+|-\)}
\begin{equation}\begin{aligned}
	-\frac{1}{2}\frac{\rho n(D) K}{\omega - \frac{D}{2} + \frac{J}{4}}\sum_{m}\sum_{k_1,k_2,l_2} J^t_m \left( J^t_{m+1} \right)^2 \ket{m}\bra{m+1}c^\dagger_{k_1 \uparrow, l_2}c_{k_2 \downarrow,l_2}
\end{aligned}\end{equation}
\paragraph{\(+|-|-\)}
\begin{equation}\begin{aligned}
	-\frac{1}{2}\frac{\rho n(D) K}{\omega - \frac{D}{2} + \frac{J}{4}}\sum_{m}\sum_{k_1,k_2,l_2} J^t_m \left( J^t_{m+1} \right)^2 \ket{m+1}\bra{m}c^\dagger_{k_1 \downarrow, l_2}c_{k_2 \uparrow,l_2}
\end{aligned}\end{equation}
\paragraph{\(-|-|+\)}
\begin{equation}\begin{aligned}
	-\frac{1}{2}\frac{\rho n(D) K}{\omega - \frac{D}{2} + \frac{J}{4}}\sum_{m}\sum_{k_1,k_2,l_2} \left( J^t_{m} \right)^2 J^t_{m+1}\ket{m+2}\bra{m+1}c^\dagger_{k_1 \downarrow, l_2}c_{k_2 \uparrow,l_2}
\end{aligned}\end{equation}
\paragraph{\(-|+|+\)}
\begin{equation}\begin{aligned}
	-\frac{1}{2}\frac{\rho n(D) K}{\omega - \frac{D}{2} + \frac{J}{4}}\sum_{m}\sum_{k_1,k_2,l_2} \left( J^t_{m} \right)^2 J^t_{m+1}\ket{m+1}\bra{m+2}c^\dagger_{k_1 \uparrow, l_2}c_{k_2 \downarrow,l_2}
\end{aligned}\end{equation}

@@

The various terms that renormalize the Hamiltonian can be described in terms of the bath spin operators that come into them. For example, the term that has \(s^z\) on both sides of the intervening Greens function can be represented as \(z|z\). There are 7 such terms: \(z|z, \pm|\mp, z|\pm, \pm|z\). Each of these terms occur both in the particle and the hole sectors.

@@

\paragraph{\(-|z\)}
\begin{equation}\begin{aligned}
	\sum_{kk^\prime,m} c^\dagger_{q \downarrow} c_{k^\prime \uparrow} \ket{m+1}\bra{m}\frac{J^\downarrow_{m}{J^t_m}}{\omega - D/2 - \frac{J}{2}S_d^z}\ket{m}\bra{m} c^\dagger_{k \downarrow}c_{q \downarrow} = -n_{q \downarrow}\sum_{kk^\prime,m}\frac{J^\downarrow_{m} J^t_m c^\dagger_{k \downarrow}c_{k^\prime\uparrow} \ket{m+1}\bra{m}}{\omega_{m, \downarrow} - D/2 - \frac{J}{2}(m)}
\end{aligned}\end{equation}
To compare with the spin-\(\frac{1}{2}\) RG equations, we will transform the general spin-\(S\) \(\omega\) to the spin-\(\frac{1}{2}\) \( \omega\), using \(\omega_{m,\sigma} \to \omega - \frac{J}{2}\left(m\sigma - \frac{1}{2}\right)\).
The first four terms renormalize \(J^\sigma_m\):
\begin{equation}\begin{aligned}
	\Delta J^\sigma_{m} = -\frac{\left( J^\sigma_m \right) ^2 + \left( J^t_{m-\frac{1+\sigma}{2}} \right) ^2}{\omega - D/2 + J/4}
\end{aligned}\end{equation}
Here, we have defined \(J^t_m = 0\) for \( |m| > S\). Two relations can be obtained from this RG equation, the RG equations for the sum and difference of the couplings. These sum and difference are defined by rewriting the Ising part of the Hamiltonian in the following fashion:
\begin{equation}\begin{aligned}
	\sum_{m=-S}^S \sum_{kl,\atop{\sigma=\uparrow,\downarrow}} J^\sigma_m \ket{m}\bra{m} c^\dagger_{k \sigma}c_{l \sigma} = \sum_{m=-S}^S \sum_{\sigma=\uparrow,\downarrow} J^+_m \ket{m}\bra{m} \sum_\sigma \hat n_{0\sigma}  + \sum_{m=-S}^S J^-_m \ket{m}\bra{m} 2s^z_0
\end{aligned}\end{equation}
where \(2J^\pm_m = J^\uparrow_m \pm J^\downarrow_m\).
The RG equation for the sum of the couplings is
\begin{equation}\begin{aligned}
	\Delta J^+_m = -\frac{1}{2}\frac{\sum_\sigma \left( J^\sigma_m \right) ^2 + \sum_\sigma \left( J^t_{m-\frac{1+\sigma}{2}} \right) ^2}{\omega - D/2 + J/4} = -\frac{J^2}{4}\frac{S(S+1)}{\omega - D/2 + J/4}
\end{aligned}\end{equation}
This is an \(m-\)independent piece, so it can be summed over to produce an impurity-independent potential scattering term:
\begin{equation}\begin{aligned}
	\sum_{m=-S}^S \sum_{\sigma=\uparrow,\downarrow} J^+ \ket{m}\bra{m} \sum_\sigma \hat n_{0\sigma} = J^+ \mathbb{I}\sum_\sigma \hat n_{0\sigma}
\end{aligned}\end{equation}
Since this term does not have any Kondo physics, we drop this piece and say that \(\Delta J^+ = 0\) and so \(\Delta J^\uparrow_m = - \Delta J^\downarrow_m \implies J^\uparrow_m = -J^\downarrow_m\) throughout the RG flow.
